### 2016-06-28 publications/Journal/4b-hotswap.tex
New order of sections
New form for the explanation of core principles of dxex
Deduplicate the section title

>>>>

%TODO explain hotswapping
%TODO why hotswapping
Simply because a synchronization protocol is ideal at the start of the simulation, does not mean that it will still be ideal during the simulation.
It has been frequently shown, and repeated in the previous section, that model behaviour significantly influences the ideal synchronization protocol.
Contrary to many modelling formalisms, the DEVS formalisms makes it possible to model basically any kind of discrete event model.
As such, it is possible for the model to significantly change its behaviour throughout the simulation.

Defining the ideal synchronization protocol at the start of the simulation, when information about future model behaviour might be scarce, might therefore not offer the best possible performance.

\subsection{Extensibility}
%TODO now purely manual
%TODO framework provided to do this using a decider
%TODO possibly using machine learning techniques

\subsection{Statistics Gathering}
%TODO traditionally only access to normal simulation state
%TODO for machine learning might give access to simulator details
%TODO such as ...

\subsubsection{Visualization of Communication}
%TODO explain simple visualizer
%TODO can be used by hotswapper
